Analysing Constraint Grammars with a SAT-solver

### 2016-03-03 paper/lrec/lrec2016_listenmaa_claessen.tex
abstract

\abstract{
We describe a method for analysing Constraint Grammars by encoding the
rules in SAT.
Our tools can detect internal conflicts or redundancies in a grammar,
as well as generate examples to demonstrate the effect of some rule or
rule set.
This can help users to diagnose and improve their grammars.
No corpus is required, only a morphological lexicon. \\ 
\newline 
\Keywords{Constrain Grammar, SAT, Grammar Analysis} }

>>>>

\abstract{
We describe a method for analysing Constraint Grammars (CG) that can detect internal conflicts and redundancies in a given grammar, without the need for a corpus. The aim is for grammar writers to be able to automatically diagnose, and then manually improve their grammars. Our method works by automatically translating the given grammar into logical constraints that are analysed by a SAT-solver. We have evaluated our analysis on a number of non-trivial grammars and found inconsistencies.
\newline 
\Keywords{Constraint Grammar, SAT, Grammar Analysis} }
